---
title: Map in R
author: Yutong Song
date: '2020-11-18'
slug: map-in-r
categories:
  - R
tags:
  - map
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval=FALSE)
library(tidyverse)
library(sf)
```

## Reading and writing spatial data in R

Download SA files in ESRI Shapefile Format from <https://www.abs.gov.au/AUSSTATS/abs@.nsf/DetailsPage/1270.0.55.001July%202016?OpenDocument>. 
Source: <https://medium.com/analytics-vidhya/mapping-australia-in-r-6ce092c48b49> 


```{r}

AUS_SA2_shp <- read_sf("data/map/1270055001_sa2_2016_aust_shape","SA2_2016_AUST")
st_write(AUS_SA2_shp, "data/sa2_dt", driver="ESRI Shapefile")

```

Another post about reading and writing spatial data <https://mgimond.github.io/Spatial/reading-and-writing-spatial-data-in-r.html#exporting-to-different-data-file-formats>

## Package comparison:

- baseR
- ggplot2
- tmap
- ggmap
- Leaflet
- mapdeck


### baseR

Source: <https://cran.r-project.org/web/packages/cancensus/vignettes/Making_maps_with_cancensus.html>


### ggplot2

Using **geom_sf** on Mac is super slow if it is even possible. People suggest to install **Quartz** on Mac OS. This post discuss performance issue of Quartz and X11. 
Source: <https://community.rstudio.com/t/ggplot2-geom-sf-performance/3251>; 
Another post: <https://stackoverflow.com/questions/51126014/why-does-tmap-render-80-times-faster-than-ggplot2-plotting-shapefiles-in-r-wit>



```{r}

library("grDevices")
## geom_sf with X11
X11(type = "cairo")
system.time(print(plt))

ggplot() +
  geom_sf(data = plt_df,
          aes(fill = value_of_focus)) +
  ggtitle("Australian 'value_of_focus' (SA2)") +
  xlab("Longitude") +
  ylab("Latitude") +
  theme_bw() +
  theme(legend.position = "right",
        legend.title = element_text("value_of_focus"))+
  scale_fill_continuous(label = scales::label_number_si())

ggsave("data/map.png", units="cm",dpi=200, device="png")

graphics.off()

```


### tmap

**tmap** is a fast generated map package that creates static maps with coloring. 
Source: <https://rpubs.com/quarcs-lab/tutorial-maps-in-r>

```{r}
library(tmap)

tm_shape(plt_df) +
  tm_polygons("val",
              style = "quantile",
              title = "Building Approval - Private - Value")

```

### ggmap

Source: <https://cengel.github.io/R-spatial/mapping.html>

### Leaflet

Leaflet can be used in Shiny app to create interactive maps. Here is an example of fill the map with a number of quantile groups of 5. An common error is that multiple quantities have the same value, and one method to solve this issue is to go through a while loop to reduce number of quantile. 
Source: <https://github.com/rstudio/leaflet/issues/94>

```{r}
quantileNum <- 5

 vals <- plt_df$val_yoy
# probs <- seq(0, 1, length.out = quantileNum)
# bins <- quantile(vals, probs, na.rm = TRUE, names = FALSE)

probs <- seq(0, 1, length.out = quantileNum + 1)
bins <- quantile(vals, probs, na.rm = TRUE, names = FALSE)
while (length(unique(bins)) != length(bins)) {
  quantileNum <- quantileNum - 1
  probs <- seq(0, 1, length.out = quantileNum + 1)
  bins <- quantile(vals, probs, na.rm = TRUE, names = FALSE)
}

pal_fun <- colorQuantile("YlOrRd", NULL, n = quantileNum)
p_popup <- paste0(plt_df$SA2_NAME16,"\n","<strong>Value: </strong>", scales::percent(plt_df$val_yoy,accuracy = 0.01))

leaflet(plt_df) %>% 
  addPolygons(
    stroke = FALSE, # remove polygon borders
    fillColor = ~pal_fun(val_yoy), # set fill color with function from above and value
    fillOpacity = 0.8, smoothFactor = 0.5, # make it nicer
    popup = p_popup  # add popup
    ) %>%
  addTiles() %>%  # add in base map
  addLegend("bottomright",  # location
            pal= pal_fun,    # palette function
            values= ~ dwl_yoy,  # value to be passed to palette function
            title = 'YOY Change by No. of Dwellings') # legend title
```

**Note**: make shiny Leaflet map faster <https://community.rstudio.com/t/make-shiny-leaflet-map-less-cumbersome-faster/210/2>

An Australia example of applying rmapshaper <https://stackoverflow.com/questions/51607487/optimising-shiny-leaflet-performance-for-detailed-maps-with-many-layers>

Leaflet markers <https://rstudio.github.io/leaflet/markers.html#marker-clusters>

Other Leaflet related posts:
- support a number of markers <https://stackoverflow.com/questions/53038090/r-leaflet-limitations-how-many-markers-does-a-leaflet-map-support>

### mapdeck

mapdeck according to <https://stackoverflow.com/questions/54613005/shiny-and-leaflet-integration-is-really-slow-how-can-i-speed-it-up> is a faster alternative to plot sf objects. The original github repo is <https://github.com/SymbolixAU/mapdeck>.


### Other supplementary sources

Source 1. Experiments with sf (spatial data in r) <https://rstudio-pubs-static.s3.amazonaws.com/488297_b0b54ede7c844e639e47dff70c028b37.html>
Source 2. Drawing beautiful maps programmatically with R, sf and ggplot2 — Part 1: Basics <https://www.r-spatial.org/r/2018/10/25/ggplot2-sf.html>
