---
title: R Saving Image Tips
author: Yutong Song
date: '2020-11-13'
slug: r-saving-image-tips
categories:
  - R
tags:
  - R
  - Shiny
series:
  - Tips
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

## Create new directory 

My habit is to create a suffix with system date to archive different versions of graphs. However, one can also use different folder names to manage archives. **dir.create** exists in base R.

```{r, eval = FALSE, echo = TRUE}
# Name a folder with name test and system date as suffix
folder_name <- str_c("test_", Sys.Date())

# Create a folder with the name set above
dir.create(folder_name)

# Create sub-folder with name subfolder1
dir.create(file.path(folder_name, "subfolder1"))
```


## Save images into the directory

Deal with saving a number of plots is to generate all plots first, name them, and then passing their names and actual plots as lists into map2. Using name as part of the file name, and the plot as the content. **ggsave** (from ggplot2 package) is super useful in this context.

```{r, eval = FALSE, echo = TRUE}
map2(names_of_plots, plots,
     ~ ggsave(str_c(folder_name, "/subfolder1/", .x, ".png"), .y,
              width = 10, height = 20))
```

